Certified Symbolic Finite Transducers: Formalization and Applications to String Manipulation

### 2025-07-20 Paper/main.tex
fix the figure

The first case can be modeled by SFTs. We illustrate this case by an example. Given a replacement operation $\texttt{replace}(s, \texttt{/[0-9]+/}, "\texttt{NUM}")$, which means replacing a occurrence of the substring that matches the regular expression $\texttt{/[0-9]+/}$ with the string "\texttt{NUM}".
We model this replacement operation by an SFT with the following 3 steps:

@@

     \path[->] 
     (q0') edge [bend left] node {\texttt{[0-9]}, $\texttt{f}$} (q1')
     (q1') edge [loop above] node {\texttt{[0-9]}, $\texttt{f}$} (q1')
     (q0') edge [loop below] node {$\Sigma$, $\texttt{id}$} (q0');

@@

    \path[->] 
    (q0'') edge node {\texttt{None}, \texttt{(g 1)}} (q1'')
    (q1'') edge [bend left=5] node[left] {\texttt{None}, \texttt{(g 2)}} (q2'')
    (q2'') edge node {\texttt{None}, \texttt{(g 3)}} (q3'')
    (q3'') edge [loop below] node {$\Sigma$, $\texttt{id}$} (q3'')
    (q1') edge [bend right=30] node {\texttt{None}, \texttt{f}} (q0'');
  \end{tikzpicture}
  \caption{The SFT for the replacement operation \\ $\texttt{replace}(s, \texttt{/[0-9]+/}, \text{``NUM''})$}
  \label{fig-rearranged-automata}
  \end{figure}

>>>>

The first case can be modeled by SFTs. We illustrate this case by an example. Given a replacement operation $\texttt{replace}\newline(s, \texttt{/[0-9]+/}, "\texttt{NUM}")$, which means replacing a occurrence of the substring that matches the regular expression $\texttt{/[0-9]+/}$ with the string "\texttt{NUM}".
We model this replacement operation by an SFT with the following 3 steps:

@@

     \path[->] 
     (q0') edge [bend left] node {\texttt{[0-9]}, $\texttt{f}$} (q1')
     (q1') edge [loop right] node {\texttt{[0-9]}, $\texttt{f}$} (q1')
     (q0') edge [loop below] node {$\Sigma$, $\texttt{id}$} (q0');

@@

    \path[->] 
    (q0'') edge node {\texttt{None}, \texttt{(g 1)}} (q1'')
    (q1'') edge [bend left=5] node[left] {\texttt{None}, \texttt{(g 2)}} (q2'')
    (q2'') edge node {\texttt{None}, \texttt{(g 3)}} (q3'')
    (q3'') edge [loop left] node {$\Sigma$, $\texttt{id}$} (q3'')
    (q1') edge [bend right=30] node {\texttt{None}, \texttt{f}} (q0'');
  \end{tikzpicture}
  \caption{The SFT for the replacement operation \\ $\texttt{replace}(s, \texttt{/[0-9]+/}, \text{``NUM''})$}
  \label{fig-rearranged-automata}
  \end{figure}
